### 2012-01-23 GUIErrorDetector/paper/technique.tex
paper revise

This section formulates our high-level approach. We define the
notations of \textit{UI thread}, \textit{non-UI threads},
\textit{UI accessing methods},
 \textit{safe methods}, and \textit{invalid thread access error}, and
two assumptions we make with regard to error detection.

@@

\noindent {\textsc{\textbf{Definition 3 (UI-Accessing Methods).}}} { A method
whose execution may read or write a UI object is called a UI accessing method.}\vspace{1mm}

@@

At a high level, to detect an invalid thread access error, an analysis needs to track all
non-UI threads spawned by the UI thread, and check whether those non-UI threads
may invoke a UI accessing method.

@@

Our algorithm in Figure~\ref{fig:detectalgorithm} works as follows. It
first constructs a static call graph for the tested program (line 2),
then specifies entry nodes for it (line 3). The algorithm starts to traverse
the call graph from every entry node (line 6). For every entry node,
it first uses Breadth First Search (BFS) to find all reachable
\CodeIn{Thread.start()} calls (line 7). Each \CodeIn{Thread.start()} call
indicates that a new, non-UI thread is spawned.  After that, 
the algorithm uses a BFS to find reachable UI accessing methods (lines 9 -- 23)
from each \CodeIn{Thread.start()} node.
Specifially, it uses a queue to keep track of all visited nodes, and
then checks every successive node to be visited (line 12);
it reports an error if that node
is a UI accessing method (line 15), or skips it if it is
a safe method (line 17), or simply keeps traversing otherwise (line 19).

If the algorithm determines that a UI accessing method may be invoked
by a non-UI thread, it creates an error report containing the full
method call chain from the entry node (line 15, the \CodeIn{createErrorReport}
method). An example call chain for
the motivating example in Figure~\ref{fig:androiderror} is shown
in Figure~\ref{fig:report}.

@@

@@

\subsubsection{Call Graph Construction}
\label{sec:cg}

@@

1. public class MyActivity extends Activity \{
2.    final List<View> cachedViews = new LinkedList<View>();
3.    @Override
4.    public void onCreate(Bundle savedInstanceState) \{
5.        super.onCreate(savedInstanceState);
6.        setContentView(R.layout.main);
7.        Button button = (Button) findViewById(R.id.\textbf{button\_id});
8.        button.setOnClickListener(new Button.OnClickListener() \{
9.            @Override
10.           public void onClick(View v) \{
11.               button.setText("Button Clicked.");
12.               cachedViews.add(v);
13.           \}
14.       \});
15.   \}
16. \}
\end{alltt}
\end{CodeOut}
\label{fig:sampleandroid}
\caption{Sample GUI application code on the Android platform. The layout
XML file (the top) specifies a Button object declaratively, 
and the Java code (the bottom)
first loads the XML file (line 6) and then uses reflection to create
a Button object by its ID (line 7, the \CodeIn{findViewById} method).}
\end{figure}

In the context of object-oriened languages wth dynamic dispatch, the
crucial step in constructing a call graph is to compute a conservative
approximation of the set of methods that can be invoked by a given
virtual method call. Call graph construction algorithms have been
studied intensively in the 1990s. While their original formulations
use a variety of formalisms, most of them can be recast as set-based
analyses. Various algorithms differ primarily in the number of sets
that are used to approximate run-time values of expressions. 
In practice, algorithms such as RTA that use a single set for the whole
program scale well but achieves relatively lower precision. The
k-CFA algorithms maintains one set per expression achieves better
precision than RTA (\textit{k} is the context length, which is
orthogonal to the number of maintained sets).

\begin{figure}[t]
\textbf{Input}: a Java program $P$, a list of classes $cls$\\
\textbf{Output}: a call graph $cg$\\
\vspace{-5mm}
\begin{algorithmic}[1]
\STATE callSiteMap $\leftarrow$ new Map$\langle$CallSite, List$\langle$Type$\rangle$$\rangle$
\STATE rta\_cg $\leftarrow$ $constructCallGraphByRTA$($P$)
\FOR{each $method$ in $P$}
\FOR{each  $callSite$ in $method$}
\STATE type $\leftarrow$ $staticType$(callSite)
\IF{type $\in$ $cls$}
\FOR{each subType of $subType$(type)}
\IF{$hasObjectCreated$(subType, rta\_cg)}
\STATE callSiteMap[callSite].add(subType)
\ENDIF
\ENDFOR
\ENDIF
\ENDFOR
\ENDFOR
\STATE $cg$ $\leftarrow$ $constructCallGraphByKCFA$($P$, callSiteMap)
\RETURN $cg$
%\ENDWHILE
\vspace{-2mm}
\end{algorithmic}
\label{fig:cgalgorithm}
\caption{A combined  RTA~\cite{rta} and k-CFA~\cite{kcfa} call graph construction algorithm.
$cls$ is a list of classes whose method invocations are added to the
call graph using the RTA algorithm; while method invocations from other classes
are added to the call graph using the k-CFA algorithm.
} 
\end{figure}

Unfortunately, GUI applications often use reflection, which makes either
RTA or k-CFA insufficient to build a satisfactory call graph. 
The example code in Figure~\ref{fig:sampleandroid}  illustrates their limitations.
In Figure~\ref{fig:sampleandroid}, line 7 uses reflection to create a \CodeIn{Button}
object by looking up its id declared in the XML file. When this button
is clicked, its event handling code (line 10 -- 13) updates the text and caches
the current view to a list declared at line 2.

Existing call graph algorithms either suffer from the problem of incompleteness
or imprecision. The k-CFA algorithm performs points-to analysis with call
graph construction interleavingly, and maintains a value set for every expression.
For example, it concludes that variable \CodeIn{cachedViews} can only point
to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
conclude that variable \CodeIn{button} declared at line 7 points to
a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
fully solve this problem. RTA adds an edge for a method invocation 
to the call graph if an object of the receiver's type (or subtype)
has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
RTA maintains a global value set for those GUI object type, and  adds a
call edge \CodeIn{setText} to the call graph. However, RTA introduces 
unnecessary precision loss: it may
may conclude that the \CodeIn{cachedViews} variable at line 2
point to any created \CodeIn{List} objects created somewhere else in the program, despite the
fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.

To alleviate the above problems, we present a combined RTA and k-CFA
call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
The algorithm shares the same spirit as k-CFA to maintain a value set
for each expression. However, the only difference is that our
algorithm uses a RTA-style treatment for constructing the value set for
GUI classes: it parses the XML configuration file and explicitly
adds a raw object to each declared GUI variable's value set. Thus,
For the example in Figure~\ref{fig:sampleandroid}, this
combined algorithm concludes that a \CodeIn{Button} object has been
created at line 7 and then adds the call edge \CodeIn{setText} to the
graph. It also concludes that the \CodeIn{cachedViews} variable can only
point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.
%For desktop applications which have main method, it is straigtforward to apply
%the above algorithm. However, for applications on platforms like eclipse plugin
%and Android. presents new challenges. Two technical challenges must be solve.
%First, use reflection extensively, Second, it is possible to interact with
%native code.

%Android features an extended event-based library and dynamic inflation of
%graphical views from declarative XML layout files.
%A static analyzer for Android programs must consider such features, for
%correctness and precision.

%Give an example of how reflection affect call graph precision.

%So, we present a new call graph construction algorithm

%reflected classes are known, use RTA.

%reflection code

%native code

\subsubsection{Heuristic Filtering and Annotation}
\label{sec:heuristic}

A static analysis can exhaustively check possible error path; but may report
paths that do not actually exist (i.e., false positives) or different paths
 that correspond to the same error (i.e., redundant warnings). We devise
a set of heuristics below to filter out likely false positives and redundant warnings.
The first two heuristics are for reducing false positives, while the
remaining ones are for removing redundant warnings.

\item \textbf{Filter Reports Containing Library Calls}. A
reported method call chain involving common Library calls
like \CodeIn{Object.toString} or \CodeIn{Runtime.shutDown} are unlikely to
be buggy, and should be filtered. In addition, a method call chain that \textit{only}
consists of library calls after the entry method is also unlikely
to reveal a valid bug, since it has no interaction with the UI. 
We encode a list of common library calls, and remove
a report if it contaiins one of them.
%Method call chain involves typical
%system methods like \CodeIn{toString} are unlikely to reveal a real bug.

\item \textbf{Filter Reports With User-Annotated Methods}. Besides general
library calls, users are also permitted
to explicitly annotate methods that will never trigger an error.
For example, the Android GUI framework provides a utility method 
\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
before executing the code; if
not, it executes the code on the UI thread using message passing.
A reported call chain containing a annotated 
can be safely removed.
%method will never cause an
%invalid thread error and should be removed.

\item \textbf{Filter Lexically Redundant Reports}. One reported method call
chain can lexically subsume another one. For example, suppose that a reported method
call chain \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
leads to a potential error, and another entry method \CodeIn{d()} calls \CodeIn{a()}.
Therefore, a static analysis might also report another method call chain
\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
that actually corresponds to the same error root as the previous one. In this case, 
 removing the second call chain would not reduce the error detection capability:
the first call chain already reveals the same error and is shorter 
for programmers to interpret.

\item \textbf{Filter Report With the Same $k$ Head Methods}. A method can call
multiple methods that access GUI objects, such as:
\begin{CodeOut}
\begin{alltt}
     public void m() \{
         accessUIObject1();
         accessUIObject2();
     \}
\end{alltt}
\end{CodeOut}
If method \CodeIn{m()} is invoked by a non-UI thread, two method call chains
only different at last few method nodes will be reported:

In fact, these two call chains correspond to the same error root: knowning
method \CodeIn{m()} is called by a non-UI thread is sufficient to understand and fix this error.
This filter compares every two reported method call chains that share the same
$k$ ($k$ is user-settable with a default value 5) head nodes, and removes the longer one.

\item \textbf{Filter Report With the Same $k$ Tail Methods}. A method
can have multiple callers, so that method call chains with the same tail are likely
to represent different ways to trigger the same error. This filter compares every
two reported method call chains that share the same 
$k$ ($k$ is user-settable with a default value 5) tail nodes, and removes the longer one.

All above filters are based on heuristics, and thus not sound in
that it may filter real bugs. However, as we will show in
the next experiment section, all these filters work well, and significantly
reduces the number of false positives and redundant reports in practice.

@@

Our static analysis will take the call relationship as indicated by this
annotation into consideration when traversing the call graph. In our experiment,
we found such an annotation was useful: one real-world bug can only be reported
with the user-provided annotations.

@@

We instantiate our error detection techniques for four popular GUI frameworks,
namely SWT, Eclipse plugin environment, Swing, and Android.
Each framework has different settings for UI thread (i.e., \textbf{call graph entry nodes}),
\textbf{UI accessing nodes}, and \textbf{safe methods}, which correspond
to lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}. We customize those
framework-specific parts as follows.

%For each framework, we customize the \textit{call graph entry nodes},
%\textit{UI accessing nodes}, and \textit{safe methods} on lines 3 -- 5 of the
%algorithm in

@@

SWT is an open source widget toolkit for Java designed to provide efficient,
portable access to the GUI facilities of the operating systems on which it is implemented.
Like a normal Java application, a SWT desktop application has a single main method
as the starting point. By default, the main method launches
the UI thread and pops up the GUI. We instantiate our technique as follows:

@@

\item \textbf{Call graph entry nodes: } the single main method

\item \textbf{UI accessing nodes: } in STW, a thread-unsafe method calls \CodeIn{Display.checkWidget}
or \CodeIn{Display.checkDevice} methods to check whether the current thread is the UI thread or not. Thus,
we treat all such methods that must be accessed in UI thread as the UI accessing nodes.
% any
%methods that calls the checking method must be invoked in the UI thread.

\item \textbf{Safe methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
and \CodeIn{Display.syncExec}) as passing (a)synchronized messages to the UI thread.
We treat these two methods as safe methods, since invoking
them from any thread are generally considered to be safe and
would not cause an invalid thread access error.

@@

An eclipse plugin is an open program. Unlike a SWT desktop application, it does not
have a main method as a single program entry point. Instead, it extends certain
extension points provided by the eclispe framework. As a plugin starts, the eclipse
framework will calls back the overrided extension points and intializes the plugin code.
We customize our technique for eclipse plugin as follows:

@@

\item \textbf{Call graph entry nodes: } due to the complexity of the eclipse architecture,
there is no rigorous way in eclipse to identify a UI thread. Here, we use a heuristic to determine call graph
entry nodes from the UI thread. As a naming convention, source code in a plugin's \CodeIn{ui}
package deals with the creation and maintainance of a plugin's GUI, and is thus
invoked by the UI thread. We conservatively treat all public methods in the \CodeIn{ui}
as call graph entry nodes.

@@

\item \textbf{UI accessing nodes} and \textbf{Safe methods} are the same as SWT.

@@

\item \textbf{Call graph entry nodes: } all overriden callback methods in the
listerner classes are called from the UI thread. We treat those callback
methods as the entry nodes.

@@

\item \textbf{UI accessing nodes:} as stated in Swing's documentation, methods
in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
\CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
treat all methods as defined in each GUI class as UI accessing nodes.

\item \textbf{Safe methods: }  Swing provides two helper methods
(\CodeIn{SwingUti-\\lities.invokeLater} and \CodeIn{SwingUtilities.invokeDelay}) to pass messages to the UI thread.
We treat these two methods as safe methods.

@@

\item \textbf{UI accessing nodes: } like SWT, Android explicitly checks the current
thread validity before accessing a GUI object using the \CodeIn{ViewRoot.checkThread} method.
Thus, we treat every methods that calls \CodeIn{ViewRoot.checkThread} as a UI accessing node
in the call graph.
%method. This method is the only place where Android checks
%whether the current thread is the UI thread or not. Thus, any
%methods that calls the checking method must be invoked in the UI thread.

>>>>

This section formulates our high-level approach. We define the
notations of \textit{UI thread}, \textit{non-UI threads},
\textit{UI-accessing methods},
 \textit{safe methods}, and \textit{invalid thread access error}, and
two assumptions we make with regard to error detection.

@@

\noindent {\textsc{\textbf{Definition 3 (UI-Accessing Methods).}}} { A method
whose execution may read or write a UI object is called a UI-accessing method.}\vspace{1mm}

@@

At a high level, to detect an invalid thread access error, an analysis needs to track all
non-UI threads spawned by the UI thread, and check whether those non-UI threads
may invoke a UI-accessing method.

@@

Our algorithm in Figure~\ref{fig:detectalgorithm} works as follows. It
first constructs a static call graph for the tested program (line 2),
then specifies entry nodes for it (line 3). The algorithm starts to traverse
the call graph from every entry node (line 6). For every entry node,
it first uses Breadth First Search (BFS) to find all reachable
\CodeIn{Thread.start()} calls (line 7). Each \CodeIn{Thread.start()} call
indicates that a new, non-UI thread is spawned.  After that, 
the algorithm uses a BFS to find reachable UI-accessing methods (lines 9 -- 23)
from each \CodeIn{Thread.start()} node.
Specifially, it uses a queue to keep track of all visited nodes, and
then checks every successive node to be visited (line 12);
it reports an error if that node
is a UI-accessing method (line 15), or skips it if it is
a safe method (line 17), or simply keeps traversing otherwise (line 19).

If the algorithm determines that a UI-accessing method may be invoked
by a non-UI thread, it creates an error report containing the full
method call chain from the entry node (line 15, the \CodeIn{createErrorReport}
method). An example call chain for
the motivating example in Figure~\ref{fig:androiderror} is shown
in Figure~\ref{fig:report}.

@@

%we augument k-CFA with value set

@@

\subsubsection{Reflection-aware Call Graph Construction}
\label{sec:cg}

%In OO program, translate k-CFA as:
%k-call-site sensitive interprocedural pointer
%analysis with a k-context-sensitive heap and onthe-
%fly call-graph construction
%

@@

1. public class MyActivity extends Activity \{
2.    @Override
3.    public void onCreate(Bundle savedInstanceState) \{
4.        super.onCreate(savedInstanceState);
5.        setContentView(R.layout.main);
6.        Button button = (Button) findViewById(R.id.\textbf{button\_id});
7.        button.setOnClickListener(new Button.OnClickListener() \{
8.            @Override
9.            public void onClick(View v) \{
10.               button.setText("Button Clicked.");
11.           \}
12.       \});
13.   \}
14. \}
\end{alltt}
\end{CodeOut}
\label{fig:sampleandroid}
\caption{Sample GUI application code on the Android platform. The layout
XML file (the top) specifies a Button object declaratively, 
and the Java code (the bottom)
first loads the XML file (line 6) and then uses reflection to create
a Button object by its ID (line 7, the \CodeIn{findViewById} method).}
\end{figure}

In the context of object-oriened languages wth dynamic dispatch, the
crucial step in constructing a call graph is to compute a conservative
approximation of the set of methods that can be invoked by a given
virtual method call. Call graph construction algorithms have been
studied intensively in the 1990s. While their original formulations
use a variety of formalisms, most of them can be recast as set-based
analyses. Various algorithms differ primarily in the number of sets
that are used to approximate run-time values of expressions. 
In practice, algorithms such as RTA that use a single set for the whole
program scale well but achieves relatively lower precision.  The
k-CFA algorithms maintains one or several sets per expression achieves better
precision than RTA (\textit{k} is length of calling context).

%this is wrong for k-CFA, k-CFA maintains several sets per expression, which k > 0
%should cite Ben Livshit's paper on "Reflection analysis for Java"
%Donot overclaim "say propose a new technique", instead, say "refine the technique"
%also need to cite Yannis's paper on solving k-CFA paradox

%\textbf{need to describe why need to traverse from the UI entry, not just from the thread entry}

\begin{figure}[t]
\textbf{Input}: a Java program $P$\\
\textbf{Output}: a call graph $cg$\\
\vspace{-5mm}
\begin{algorithmic}[1]
\FOR{each $statement$ in $P$}
\IF{$statement$ is a reflection call}
\STATE objectSet $\leftarrow$ getAllObjectsToCreate($statement$)
\STATE $newInstr$ $\leftarrow$ createObjectCreationStatement(objectSet)
\STATE replace $statement$ with $newInstr$
\ENDIF
\ENDFOR
\STATE $cg$ $\leftarrow$ $constructCallGraph$($P$, callSiteMap)
\RETURN $cg$
%\ENDWHILE
\vspace{-2mm}
\end{algorithmic}
\label{fig:cgalgorithm}
\caption{A reflection-aware call graph construction algorithm. Lines 1
- 7 shows a simple program transformation to replace reflection calls
with object creations, and line 8 constructs the call graph on
the transformed program using the existing call graph algorithm. 
} 
\end{figure}

Unfortunately, GUI applications often use reflection extensively and make
existing call graph construction algorithms fail to build a sufficiently complete
call graph. The example code in Figure~\ref{fig:sampleandroid} from an Android application
 illustrates the limitations.
In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
object by looking up its id declared in the XML file. When this button
is clicked, its event handling code (line 9 -- 11) updates the text.
%d caches
%the current view to a list declared at line 2.

When using existing call graph algorithms to analyze the code in Figure~\ref{fig:sampleandroid},
they fail to conclude that variable \CodeIn{button} declared at line 7
point to a \CodeIn{Button} object due to its limitation in deal with the
reflection call \CodeIn{findViewById}. Thus, the resulting
call graph will miss the calling edge corresponding to the method
call \CodeIn{setText} at line 10.

%Existing call graph algorithms failed either suffer from the problem of incompleteness
%or imprecision. The k-CFA algorithm performs points-to analysis with call
%graph construction interleavingly, and maintains a value set for every expression.
%For example, it concludes that variable \CodeIn{cachedViews} can only point
%to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
%can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
%conclude that variable \CodeIn{button} declared at line 7 points to
%a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
%may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
%On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
%fully solve this problem. RTA adds an edge for a method invocation 
%to the call graph if an object of the receiver's type (or subtype)
%has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
%RTA maintains a global value set for those GUI object type, and  adds a
%call edge \CodeIn{setText} to the call graph. However, RTA introduces 
%unnecessary precision loss: it may
%may conclude that the \CodeIn{cachedViews} variable at line 2
%point to any created \CodeIn{List} objects created somewhere else in the program, despite the
%fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.

To alleviate this limitation, we present an algorithm to construct
a reflection-aware call graph based on simple program transformation.
The basic idea to replace reflection calls with explicit object
creation instructions, pretending the corresponding concreate object
has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
It consists of two steps. The first step is a simple program
transformation to replace reflection calls with object creations, and
the second step is to use standard call graph construction algorithms
to construct the graph on the transformed program. Lines 1 - 7 show
the transformation step. The algorithm iterates through every statement
in an analyzed program. When it sees a reflection call statement (e.g.,
the \CodeIn{findViewById} method), the algorithm analyzes the
program to determine a set of possible classes that may be created.
After that, the algorithm creates a new instruction which non-deterministically
returns a new object of the class set. The reflection-aware call graph
construction algorithm is indepdent of the underlying call graph algorithm;
any existing algorithm can be used to construct the resulting graph at line 8.

For the example in Figure~\ref{fig:sampleandroid}, the algorithm
first parses the XML configuration file to determine that the \CodeIn{button\_id}
value is mapped to a \CodeIn{Button} instance declaration. Then it
replaces the \CodeIn{findViewById(R.id.button\_id)} method call 
with an explicit object creation instruction \CodeIn{new Button}.
After that, the algorithm employs existing call graph construction
algorithms to analyze the transformed program, and permits them
to add the call edge \CodeIn{setText} to the resulting graph.

Using this reflection-aware call graph construction algorithm is
critical to detect bugs on realistic GUI applications.
As demonstrated in our experiments, errors in all Android applications
can only be detected using this algorithm.

% combined RTA and k-CFA
%call graph construction algorithm as shown in Figure~\ref{fig:cgalgorithm}.
%The algorithm shares the same spirit as k-CFA to maintain a value set
%for each expression. However, the only difference is that our
%algorithm uses a RTA-style treatment for constructing the value set for
%GUI classes: it parses the XML configuration file and explicitly
%adds a raw object to each declared GUI variable's value set. Thus,
%For the example in Figure~\ref{fig:sampleandroid}, this
%combined algorithm concludes that a \CodeIn{Button} object has been
%created at line 7 and then adds the call edge \CodeIn{setText} to the
%graph. It also concludes that the \CodeIn{cachedViews} variable can only
%point to a \CodeIn{LinkedList} object, avoiding unnecessary precision loss.

\subsubsection{Annotation for Native Methods}

@@

Our static analysis will also take the call relationship as indicated by this
annotation into consideration when traversing the call graph. In our experiment,
we found such an annotation was useful: one real-world bug can only be reported
with the user-provided annotations.

\subsubsection{Heuristic Filtering}
\label{sec:heuristic}

A static analysis can exhaustively check possible error path; but may report
paths that do not actually exist (i.e., false positives) or multiple paths
 that have the same error cause (i.e., redundant warnings). We devise
5 heuristics below to remove likely false positives and redundant warnings.
The first two are for eliminating false positives, while the
other three are for reducing redundant warnings.

\item \textbf{Filter Reports Containing Library Calls}. A
method call chain involving normal library calls
like \CodeIn{Object.toString} or \CodeIn{Runtime.shutDown} are unlikely to
be buggy. In addition, a method call chain that \textit{only}
consists of library calls after the entry method is also unlikely
to reveal a valid bug, since it has no UI interaction.
We encode a list of common library calls, and remove
a reported warning if it contains one of them.
%Method call chain involves typical
%system methods like \CodeIn{toString} are unlikely to reveal a real bug.

\item \textbf{Filter Reports With User-Annotated Methods}. Besides general
library calls, users are also permitted
to explicitly annotate methods that will never trigger an error.
For example, the Android GUI framework provides a utility method 
\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
before executing the code. If the current thread is not the UI thread,
this method will be executed on the UI thread via message passing.
Thus, a reported method call chain containing an annotated 
can be safely removed.
%method will never cause an
%invalid thread error and should be removed.

\item \textbf{Filter Lexically Redundant Reports}. One reported method call
chain can lexically subsume another one. For example, suppose that two
reported method call chains: \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
$\rightarrow$ \CodeIn{c()} and 
\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
are two separated entry methods. The second call chain should
be removed and would not reduce the error detection capability, since
the first chain reveals the same error and is shorter 
for programmers to interpret.

\item \textbf{Filter Report With the Same $k$ Head Methods}. A method can call
multiple methods that access GUI objects, such as:
\begin{CodeOut}
\begin{alltt}
     public void m() \{
         accessUIObject1();
         accessUIObject2();
     \}
\end{alltt}
\end{CodeOut}
If method \CodeIn{m()} is invoked by a non-UI thread, method call chains
only different at the last few method nodes may be reported separately, such as:

In fact, these two chains may have the same error root: knowning that
method \CodeIn{m()} is called by a non-UI thread is sufficient to understand
the error.
This filter compares two reported chains that have the same
$k$ ($k$ is user-settable with a default value 5) head nodes, and removes the longer one.

\item \textbf{Filter Report With the Same $k$ Tail Methods}. A method
can have multiple callers, so that method call chains with the same tail are likely
to just represent different ways to trigger the same error. This filter compares 
two reported method call chains that share the same 
$k$ ($k$ is user-settable with a default value 5) tail nodes, and removes the longer one.

All above 5 filters are based on heuristics, and thus are not sound in
that it may filter real bugs. However, as we will show in
our experiments, these filters work remarkably well in
reducing the number of false positives and redundant reports in practice.

@@

We instantiate our error detection techniques for four popular GUI frameworks,
namely SWT, Eclipse plugin environment, Swing, and Android.
The major framework-specific parts, corresponding to
lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are to identify
\textbf{call graph entry nodes}), \textbf{UI-accessing nodes},
and \textbf{safe methods} for each framework.

%For each framework, we customize the \textit{call graph entry nodes},
%\textit{UI-accessing nodes}, and \textit{safe methods} on lines 3 -- 5 of the
%algorithm in

@@

%SWT is an open source widget toolkit for Java designed to provide efficient,
%portable access to the GUI facilities of the operating systems
%on which it is implemented.
Like a normal Java application, a SWT desktop application
has a single main method as the entry point. By default,
the main method launches the UI thread when initializing the GUI.
We instantiate our technique for SWT applications as follows:

@@

\item \textbf{Call graph entry nodes: } the main method

\item \textbf{UI-accessing nodes: } SWT provides explicit
runtime checking for illegal thread access. Any methods for manipulating
GUI object must call methods \CodeIn{Display.checkWidget}
or \CodeIn{Display.checkDevice} to check whether the current
thread is the UI thread or not.
Thus, we treat nodes corresponding to the methods
calling these two methods as UI-accessing nodes.
%must be invoked
%in the UI thread and as
%UI-accessing nodes.
 %methods to check whether the current thread is the UI thread or not. Thus,
%we treat all such methods that must be accessed in UI thread as the UI-accessing nodes.
% any
%methods that calls the checking method must be invoked in the UI thread.

\item \textbf{Safe methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
and \CodeIn{Display.syncExec}) to execute code (a)synchronizedly on the UI thread.
We treat these two methods as safe methods, since invoking
them from any thread 
%are generally considered to be safe and
would not cause an invalid thread access error.

@@

%An eclipse plugin is an open program. 
Unlike a SWT desktop application, an Eclipse plugin does not
have a main method as a single program entry point. Instead, it extends
extension points provided by the Eclispe framework to implement
functionalities. When a plugin starts, Eclipse
calls back the overrided extension points to handle the
upcoming events. We customize our technique for Eclipse plugin as follows:

@@

\item \textbf{Call graph entry nodes: } all overriden SWT
GUI event handling methods\footnote{Eclipse plugin is built
on top of the SWT framework} are called from the UI thread.
We treat these callback methods as the entry nodes.

%due to the complexity of the eclipse
%architecture,
%there is no rigorous way in eclipse to identify a UI thread. Here, we use a heuristic to determine call graph
%entry nodes from the UI thread. As a naming convention, source code in a plugin's \CodeIn{ui}
%package deals with the creation and maintainance of a plugin's GUI, and is thus
%invoked by the UI thread. We conservatively treat all public methods in the \CodeIn{ui}
%as call graph entry nodes.

@@

\item \textbf{UI-accessing nodes} and \textbf{Safe methods} are the same as SWT.

@@

\item \textbf{Call graph entry nodes: } all overriden callback methods in 
Swing's UI listerner classes are called from the UI thread. We treat those callback
methods as the entry nodes.

@@

\item \textbf{UI-accessing nodes:} as stated in Swing's documentation, methods
in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
\CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
treat all methods defined in each GUI class as UI-accessing nodes.

\item \textbf{Safe methods: }  Swing provides two helper methods
(\CodeIn{SwingUti-\\lities.invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) to pass messages to the UI thread.
We treat these two methods as safe methods.

@@

\item \textbf{UI-accessing nodes: } like SWT, Android explicitly checks whether
the current thread is a UI thread or not before accessing a GUI object via
the \CodeIn{ViewRoot.checkThread} method.
Thus, we treat every methods calling \CodeIn{ViewRoot.checkThread} as a UI-accessing node
in the call graph.
%method. This method is the only place where Android checks
%whether the current thread is the UI thread or not. Thus, any
%methods that calls the checking method must be invoked in the UI thread.
